Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-02-18 xrb/submit/paper.tex
Update paragraph comparing with Yuri's papers

@@

We explore the baroclinic instability by looking at the magnitude of the 
baroclinicity, calculated as
\begin{equation}
    \boldsymbol{\psi} = \frac{1}{\rho^2} \nablab p \times \nablab \rho,
\end{equation}
and shows the misalignment of the local density and pressure gradients
(we also explored this in \citealt{Malone2014a}). As we are considering a 2D system, the
component of the baroclinicity we consider here (out of the plane)
reflects the misalignment of the fields in the plane of the
simulation. Figure~\ref{fig:baroclinicity} shows that the
baroclinicity peaks along the flame front. This baroclinicity
generates vorticity, which in turn entrains material along the surface
of the flame (see also \citealt{cavecchi:2013}). In 3D, this same vorticity
should perturb the flame front and further increase the flame speed
\citep{Cavecchi2019}.

>>>>

The computational expense of the problem necessitated several approximations
to make this set of simulations \citep{cavecchi:2013, art-2015-cavecchi-etal, art-2016-cavecchi-etal, Cavecchi2019}
tractable. The first was the assumption of vertical hydrostatic equilibrium, which
allowed them to filter out vertically propagating sound waves that would otherwise
have limited the timestep. This enabled them to reach the simulation times (on the
order of seconds) needed to capture the rise of the burst, but they could not model
vortical fluid motions driven by effects such as turbulence and convection. These can
facilitate mixing and help to accelerate the propagation of the flame front. They also
included only the triple-$\alpha$ process in their implementation of nuclear burning,
and use a fixed, constant opacity across the entire domain for each simulation run (although
they explore the dependence of the flame propagation speed on this opacity value).
Our simulations relax the assumption of vertical hydrostatic equilibrium, and implement
a more complete set of nuclear reactions and opacities. However, this comes at the expense
of a different set of approximations.

@@

We explore the baroclinic instability by looking at the magnitude of the 
baroclinicity, calculated as
\begin{equation}
    \boldsymbol{\psi} = \frac{1}{\rho^2} \nablab p \times \nablab \rho,
\end{equation}
and shows the misalignment of the local density and pressure gradients
(we also explored this in \citealt{Malone2014a}). As we are considering a 2D system, the
component of the baroclinicity we consider here (out of the plane)
reflects the misalignment of the fields in the plane of the
simulation. Figure~\ref{fig:baroclinicity} shows that the
baroclinicity peaks along the flame front. This baroclinicity
generates vorticity, which in turn entrains material along the surface
of the flame (as seen in \citealt{cavecchi:2013}). In 3D, this same vorticity
should perturb the flame front and further increase the flame speed
\citep{Cavecchi2019}.
